A general and efficient representation of Ancestral Recombination Graphs

### 2022-07-15 paper.tex

@@

\section*{Genome ARGs}
% We're not the first to talk about ARGs and pedigrees, and we're
% not doing anything controversial.
The deep connection between ARGs and pedigrees is
well known
\citep[e.g.][]{wakeley2012genetics,gusfield2014recombinatorics,
speed2015naturereviewsgenetics}
and recent discussions have illustrated the
relationship~\citep{mathieson2020ancestry,brandt2021evaluation}, % more??
showing how the coalescence and recombination events in an ARG
correspond to particular genomes in the pedigree.
As discussed in the previous section, the definition of an ARG
as a \emph{data structure} in terms of these two events is problematic,
fundamentally limiting the patterns of ancestry that can be described.
Following \cite{mathieson2020ancestry} instead of focussing on events,
we define the ARG data structure in terms of \emph{genomes} and the
patterns of transmission between them.
% Bit of duplication here, but good to make the point about being
% motivated by real existing datasets not some academic desire to
% model complexity that isn't there.
This, coupled with
the explicit association of genome coordinates with edges, allows
us to represent even the bewilderingly complex patterns of relatedness
present in modern datasets.

@@

\textcolor{red}{Discussion below on phylogenetic networks: we need to
reduce the text below down to one paragraph, which
defines the relationship between what we define as an ARG and
what people mean by phylogenetic networks from the literature.
We probably don't need to get into quite so much detail on
the different types that people have studies. Essentially,
we're ending the section with a brief review which situates
our definition in the literature. I think pulling apart the
idea of a ``reticulation'' vs what we call a recombinant
is essential here.}

>>>>

\textcolor{red}{TODO: reduce the text below down to one paragraph, which
defines the relationship between what we define as an ARG and
what people mean by phylogenetic networks from the literature.
We probably don't need to get into quite so much detail on
the different types that people have studies. Essentially,
we're ending the section with a brief review which situates
our definition in the literature. I think pulling apart the
idea of a ``reticulation'' vs what we call a recombinant
is essential here.}

@@

\section*{Genome ARGs}
% We're not the first to talk about ARGs and pedigrees, and we're
% not doing anything controversial.
The deep connection between ARGs and pedigrees is of course
well known
\citep[e.g.][]{wakeley2012genetics,gusfield2014recombinatorics,
speed2015naturereviewsgenetics}
and recent discussions have illustrated the
relationship~\citep{mathieson2020ancestry,brandt2021evaluation}, % more??
showing how the coalescence and recombination events in an ARG
correspond to particular genomes in the pedigree.
As discussed in the previous section, the definition of an ARG
as a \emph{data structure} in terms of these two events is problematic,
fundamentally limiting the patterns of ancestry that can be described.
Following \cite{mathieson2020ancestry} instead of focussing on events,
we define the ARG data structure in terms of \emph{genomes} and the
patterns of transmission between them.
% Bit of duplication here, but good to make the point about being
% motivated by real existing datasets not some academic desire to
% model complexity that isn't there.
This, coupled with
the explicit association of genome coordinates with edges, allows
us to represent even the bewilderingly complex patterns of relatedness
present in modern datasets.

@@
